%%% AUTHOR: OZLEM

\newpage

\section{Conceptual Model For Software Design Descriptions }

\subsection{Software Design In Context}
\paragraph{}
\normalsize
The aim of this project is visualizing the fMRI data on a 3D graph to increase the understandability of the complex data. The fMRI data includes the brain response of a human due to some particular circumstances as showing the picture of a red apple.\\

The main role of the final 3D graph will be visualizing voxels and edges which show the related voxels. Besides graph may include a brain image as background and five main lobes of the brain,  which are frontal, parietal, occipital, limbic, temporal lobes, in different colors.\\
 
Since the fMRI data is very large and complex, time and space will be main constraints.\\

The target audience of this project is mostly academicians and medical institutes. Cognitive state representaion and visualization of human brain is fundamentally important in neuroanatomy, neurodevelopment, cognitive neuroscience and neuropsychology.\\

This project will be implemented with C++ as programming language, OpenGL as API and Unity3D game engine to render 3D graphics.
\skipsubsection
    

\subsection{Software Design Descriptions Within The Life Cycle}

\subsubsection{Influences on SDD Preparation}
\paragraph{}
\normalsize
     The key software life cycle product that drives a software design is typically the software requirements specification.\\
     
     The requirements in the SRS like product perspective,interface requirements, functional and non-functional requirements and also the demands of the stakeholders specify the design of the project.

\skipsubsection

\subsubsection{Influences on Software Life Cycle Products}
\paragraph{}
\normalsize
	As said before, the key software life cycle product that drives a software design is typically the software requirements specification. However during the preparation of this Software Design Description document or the implementation stage of the project, some requirements may change and this results in the change of SRS and SDD.\\

	Besides, SDD influences test plans and test documentation of the Cognitive State Representation and Visualization of Human Brain project.

\skipsubsection

\subsubsection{Design Verification and Design Role in Validation}
\paragraph{}
\normalsize
	Verification and validation will be tested after preparation of the test cases. All system parts will be tested against these cases. It will be checked for whether the requirements fulfilled or not. 

\skipsubsection
    

