%%% AUTHOR: ATAKAN

\subsection{Context Viewpoint}
\paragraph{}
\normalsize
    This section of Software Design Document focuses on the services provided. The context is defined by reference to actors.
    \begin{center}
	\begin{tikzpicture}
      \begin{umlsystem}{Cognitive State Representation and Visualization of Human Brain} 
      	\umlusecase[x=10, y=-6]{Load File} 
        \umlusecase[x=10, y=-4.5]{Zoom In and Out}
        \umlusecase[x=10, y=-3]{Rotate}
        \umlusecase[x=10, y=-1.5]{Four Regions}
        \umlusecase[x=10, y=0]{Show Side-by-Side}
        \umlusecase[x=10, y=1.5]{Configure Colors}
        \umlusecase[x=10, y=3]{Transparency Adjustment}
        \umlusecase[x=10, y=4.5]{Change Voxel Size}
        \umlusecase[x=10, y=6]{Layer Depth Adjustment}
      \end{umlsystem} 
      
      \umlactor[x=0, y=0, scale=2]{user} 
      
      \umlassoc{user}{usecase-1}  
      \umlassoc{user}{usecase-2}  
      \umlassoc{user}{usecase-3}  
      \umlassoc{user}{usecase-4}  
      \umlassoc{user}{usecase-5}  
      \umlassoc{user}{usecase-6}  
      \umlassoc{user}{usecase-7}  
      \umlassoc{user}{usecase-8}
      \umlassoc{user}{usecase-9}  
	\end{tikzpicture}
    \end{center}
    
    
\skipsubsection


\subsubsection{Design Concerns}
\paragraph{}
\normalsize
    The use cases provided in this section depicts the offered services for the actor.
\skipsubsection


\subsubsection{Design Elements}
\paragraph{}
\normalsize
    \textbf{Actors} \\
    \begin{itemize}
    	\item User: The user that uses the program
    \end{itemize}
    
    \textbf{Services} \\
    \begin{itemize}
    	\item Load File: The user loads the data taken from fMRI machine.
        \item Zoom In and Out: The user can zoom in and zoom out to 3D image of the brain.
        \item Rotation: The user can rotate the image 360 degree around it's center to any direction.
        \item Four Regions: The user can do selection between four brain lobes. Only the selected lobes will be visible.
        \item Show Side-by-Side: With this feature, the user can see the brain from different sides in one window.
        \item Configure Colors: Changes color distribution for color blinds.
        \item Transparency Adjustment: Changes transparentcy of the voxels so deeper layers can be seen.
        \item Change Voxel Size: Changes unit size of voxels in case size is miscalulated.
        \item Layer Depth Adjustment: Allows user to view inner layers of brain.
        
    \end{itemize}
    
\skipsubsection


\subsubsection{Example Languages}
\paragraph{}
\normalsize
    In this section, UML Use Case Diagrams are used.
\skipsubsection
